Precise Data Flow Analysis\\in the Presence of Correlated Method Calls

### 2014-12-16 content/appendix.tex
changing proof of lemma 5

\begin{lemma}\label{lem:sound3}
  Let $p=[\startmain,\,\dots,\,n]$ be a concrete execution path, $r\in R$ a receiver, and $d\in D$ a data-flow fact. Then if $d\in M_F(p)(\varnothing)$,
  \begin{equation}
    \mpd(r)\ne\top_T\,.
  \end{equation}
\end{lemma}
\begin{proof}
  By induction on the length of the execution trace.

@@

  \textit{Induction hypothesis:} 
  Let $p=[\startmain,\,\dots,\,n_{k-1}]$. Let $\uptau$ be the set of types to which $r$ is mapped by $\mpdkm$:
  \begin{equation}
    \uptau=\mpdkm(r)\,.
  \end{equation}
  Assume the Lemma holds for that for a concrete execution path $$p=[\startmain,\,n_1,\,\dots,\,n_{k-1}]\,,$$ i.e. $\uptau\ne\top_T$ for an arbitrary $r\in R$ and $d_{k-1}\in D$.

@@

\precision*
\begin{proof}
    \otodo{It's Section 3.2.}
    \mtodo{Section 3.2 talks about the IFDS algorithm, but it doesn't explicitly say how the result of an IFDS analysis looks like and doesn't introduce the notation $\resultIFDS$.}
  Let $P$ be an IFDS problem. Recall from Section~\ref{sec:ideToIfds} that the result of an IFDS analysis $\resultIFDS(P)$ maps supergraph
  nodes $n\in N^*$ to sets of data-flow facts $\delta\in2^D$. Specifically,
  \begin{equation}
    \resultIFDS(P)=\lambda n\,.\,\mvp F(n)\,.
  \end{equation}
  \otodo{Where do we mention $\backEq$ in this lemma?}
  %The transformation $\backCC$ is the same as $\backEq$, except that it can remove data-flow facts from the result:
  An IFDS result The transformation $\backCC$ is the same as $\backEq$, except that it can remove data-flow facts from the result:
  \begin{align*}
    \backCC\left(\resultIDE(\transCC_R(P))\right)(n)
    &=\left(\lambda n'\,.\,\left\{d\,|\,\forall r\in R\,.\,\resultIDE(\transCC_R(P))(n')(d)(r)\ne\top_T\right\}\right)(n)\\
    &=\left\{d\,|\,\forall r\in R\,.\,\resultIDE(\transCC_R(P))(n')(d)(r)\ne\top_T\right\}\\
    &\subseteq\left\{d\,|\,\resultIDE(\transCC_R(P))(n)(d)\ne\topcc\right\}\\
    &=\backEq\left(\resultIDE(\transCC_R(P))(n)\right).\qedhere
  \end{align*}
\end{proof}

>>>>

\begin{lemma}\label{lem:sound3}
  Let $p=[\startmain,\,\dots,\,n]$ be a concrete execution path, $r\in R$ a receiver, and $d\in D$ a data-flow fact. Then
  \begin{equation}
    d\in M_F(p)(\varnothing)\iff\mpd(r)\ne\top_T\,.
  \end{equation}\mtodo{Prove other direction}
\end{lemma}
\begin{proof}
  By induction on the length of the execution trace.

@@

  \textit{Induction hypothesis:} 
  Let $p=[\startmain,\,\dots,\,n_{k-1}]$. Let $\uptau$ be the set of types to which $r$ is mapped by $\mpdkm$:
  \begin{equation}
    \uptau=\mpdkm(r)\,.
  \end{equation}
  Assume the Lemma holds for a concrete execution path $$p=[\startmain,\,n_1,\,\dots,\,n_{k-1}]\,,$$ i.e. $\uptau\ne\top_T$ for an arbitrary $r\in R$ and $d_{k-1}\in D$.

@@

\precision*
\begin{proof}
    \otodo{It's Section 3.2.}
    \mtodo{Section 3.2 talks about the IFDS algorithm, but it doesn't explicitly say how the result of an IFDS analysis looks like and doesn't introduce the notation $\resultIFDS$.}
  Let $P$ be an IFDS problem. Recall from Section~\ref{sec:ideToIfds} that the result of an IFDS analysis $\resultIFDS(P)$ maps supergraph
  nodes $n\in N^*$ to sets of data-flow facts $\delta\in2^D$. Specifically,
  \begin{align*}
    \resultIFDS(P)&=\lambda n\,.\,\mvp F(n)\\
    &=\bigsqcap_{q\in\textsf{VP}(n)}M_F(q)(\top).
  \end{align*}
  At the same time,
  \begin{align*}
    \backCC\left(\resultIDE(\transCC_R(P))\right)(n)
    &=\left(\lambda n\,.\,\left\{d\,|\,\forall r\in R\,.\,\resultIDE(\transCC_R(P))(n)(d)(r)\ne\top_T\right\}\right)(n)\\
    &=\left\{d\,|\,\forall r\in R\,.\,\resultIDE(\transCC_R(P))(n)(d)(r)\ne\top_T\right\}\\
    &=\left\{d\,|\,\forall r\in R\,.\,\bigsqcap_{q\in\textsf{VP}(n)}\xi(q,\,d)(r)\ne\top_T\right\}.
  \end{align*}
  This means that for each $d\in\backCC(\resultIDE(\transCC R(P)))(n)$ and for each path $q\in\textsf{VP}(n)$, $\xi(q,\,d)\ne\top_T$. Therefore, according to~Lemma~\ref{lem:sound3}, for each $q$, $d\in M_F(q)(\top)$. It follows that $d\in\bigsqcap_{q\in\textsf{VP}(n)}M_F(q)(\top)=\resultIFDS(P)(n)$. 
  In other words, if $d\in\backCC(\resultIDE(\transCC R(P)))(n)$, then $d\in\resultIFDS(P)(n)$.
\end{proof}
